---
title: "Slides"
author: "Mrinalini"
date: "11/4/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## What was asked

This project required me to create a presentation with the help of R Markdown where the final output would have a plot made using plotly. Please use arrow keys to go to next/previous slide

## Harry Potter
In this project I am creating a plot that shows the different books in the Harry Potter Series and the number of pages in each one of them. Please use arrow keys to go to next/previous slide

```{r include=FALSE}
library(plotly)
```
```{r}
x<- c("Philosopher's Stone","Chamber of Secrets","Prisoner of Azkaban","Goblet of Fire","Order of Phoenix","Half Blood Prince","Deathly Hallows")
books<-factor(x,levels=c("Philosopher's Stone","Chamber of Secrets","Prisoner of Azkaban","Goblet of Fire","Order of Phoenix","Half Blood Prince","Deathly Hallows"))
pgs<-c(223,251,317,636,766,652,607)
hp<-data.frame(books,pgs)
```
## Bar Graph using Plotly
```{r warning=FALSE}
plot_ly(data = hp, x = ~books, y = ~pgs,type = "bar") %>%
  layout(title = "Harry Potter Book Names and their Page Numbers",
         xaxis=list(title="Book Name"),
         yaxis=list(title="Page Numbers"))
```

